Work Fragmentation in Developer Interaction Data

### 2016-07-22 paper_2.tex
Review 3.6

A first challenge that we encountered was that, similarly to the earlier research questions, the high number of different commands made it hard to infer broader trends. We hence created an additional classification of the commands we encountered in the activity logs. In a similar manner to the first classification, we followed an iterative process involving two of the authors to classify the events in these categories. Differently to the first classification, we did not limit ourselves to a restricted number of categories: rather, we let the classification emerge from the iterative process. We ended up with 11 categories, as described in Table \ref{tbl:new_events_udc}.

@@

%\begin{table}[ht!]
%\tiny
%\renewcommand{\arraystretch}{1.3}
%\caption{New category of events. }
%\label{tbl:new_events_udc}
%\centering
%\begin{tabular}{|p{2.5cm}|p{6 cm}| p{1cm} |}
%  \hline 
%category & description & usage (\%)\\  
%  \hline 
%    \hline 
%    high-nav & High-level navigation through classes, windows and artifacts & 25.9 \\
%    edit-text & Text edition events & 19.7 \\
%    debug & Events executed during debugging sessions & 11.7 \\
%    text-nav & Low-level text navigation & 9.4 \\
%    file & Management of files (saving, closing, opening, etc.) &	8.9 \\
%    control & Source control events & 7.6 \\
%    refactoring & Refactoring events & 5.1\\
%    perspective & Change of perspectives in Eclipse & 4.1  \\
%    search & Text or code search & 2.8 \\
%    find-replace & Search and replacement of text or code entities & 2.5 \\
%    clean-build &  Events related to the build system (clean, build or run a project) & 2.3\\
%\hline
%\end{tabular}
%\end{table}

\begin{table}[ht!]
	\small
	\renewcommand{\arraystretch}{1.3}
	\caption{New category of events. }
	\label{tbl:new_events_udc}
	\centering
	\begin{tabular}{|p{2.5cm}|p{10 cm}| } %p{2cm} |}
		\hline 
		category & description \\ %& frequency \\  
		\hline 
		\hline 
		high-nav & High-level navigation through classes, windows and artifacts \\ %& 9.1 \\
		file & Management of files (saving, closing, opening, etc.) \\ %&	8.9 \\
		edit-text & Text edition events \\ %& 8.1 \\
		debug & Events executed during debugging sessions \\ %& 3.3 \\
		text-nav & Low-level text navigation \\ %& 3.1 \\
		search & Text or code search \\ %& 0.6 \\
		find-replace & Search and replacement of text or code entities \\ %& 0.6 \\
		perspective & Change of perspectives in Eclipse \\ %& 0.5  \\
		control & Source control events \\ %& 0.4 \\
		refactoring & Refactoring events \\ %& 0.3\\
		clean-build &  Events related to the build system (clean, build or run a project) \\ %& 0.2\\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[ht!]
\small
\renewcommand{\arraystretch}{1.3}
\caption{Weighted frequency of execution after positive or negative interruptions. }
\label{tbl:stats_events}
\centering
\begin{tabular}{|p{3cm}|p{2cm} |p{2cm}|p{2cm}|} 
  \hline 
category & positive & negative & all \\  
  \hline 
\multicolumn{4}{c}{\textit{Most common events after a positive interruption}} \\
    \hline 
edit-text &  \textbf{34.75} & 22.35 & 26.62 \\
file &  \textbf{10.56} & 9.53 & 10.01\\
refactoring & \textbf{1.29} & 0.84 & 1.01 \\
perspective & \textbf{0.38} & 0.30 & 0.35  \\
    \hline 
\multicolumn{4}{c}{\textit{Most common events after a negative interruption}} \\
    \hline 
high-nav & 7.84 & \textbf{10.14} & 8.74  \\
find-replace & 1.26 & \textbf{1.47} & 1.11 \\
debug & 3.08 & \textbf{7.81} & 6.35  \\
search & 0.57 & \textbf{0.96} & 0.73 \\
clean-build & 0.42 & \textbf{0.62} & 0.56  \\
    \hline 
\multicolumn{4}{c}{\textit{Less common events after a positive or negative interruption}} \\
    \hline 
text-nav & 14.20 & 12.89 & \textbf{16.13} \\
control & 1.21 & 1.75 & \textbf{1.82} \\
\hline
\end{tabular}
\end{table}

>>>>

A first challenge that we encountered was that, similarly to the earlier research questions, the high number of different commands made it hard to infer broader trends. We hence created an additional classification of the commands we encountered in the activity logs. In a similar manner to the first classification, we followed an iterative process involving two of the authors to classify the events in these categories. Differently to the first classification, we did not limit ourselves to a restricted number of categories: rather, we let the classification emerge from the iterative process. We ended up with 11 categories, as described in Table \ref{tbl:new_events_udc}. We assigned the label and description that better suited the events grouped on that category and the associated type that reflects the majority of those events.

@@

\begin{table}[ht!]
	\small
	\renewcommand{\arraystretch}{1.3}
	\caption{New category of events. }
	\label{tbl:new_events_udc}
	\centering
	\begin{tabular}{|p{2.5cm}|p{9 cm}| p{2cm} |}
		\hline 
		category & description & type \\  
		\hline 
		\hline 
		high-nav & High-level navigation through classes, windows and artifacts & navigation \\
		file & Management of files (saving, closing, opening, etc.) & navigation\\
		edit-text & Text edition events & edition \\
		debug & Events executed during debugging sessions & navigation \\
		text-nav & Low-level text navigation & edition \\
		search & Text or code search & navigation \\
		find-replace & Search and replacement of text or code entities & navigation\\
		perspective & Change of perspectives in Eclipse & navigation  \\
		control & Source control events & navigation \\
		refactoring & Refactoring events & edition \\
		clean-build &  Events related to the build system (clean, build or run a project)  & navigation \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[ht!]
\small
\renewcommand{\arraystretch}{1.3}
\caption{Weighted frequency of execution after positive or negative interruptions. }
\label{tbl:stats_events}
\centering
\begin{tabular}{|p{3cm}|p{2cm} |p{2cm}|p{2cm}|} 
  \hline 
category & positive & negative & all \\  
  \hline 
\multicolumn{4}{c}{\textit{Categories that are more frequent after a positive interruption}} \\
    \hline 
edit-text &  \textbf{34.75} & 22.35 & 26.62 \\
file &  \textbf{10.56} & 9.53 & 10.01\\
refactoring & \textbf{1.29} & 0.84 & 1.01 \\
perspective & \textbf{0.38} & 0.30 & 0.35  \\
    \hline 
\multicolumn{4}{c}{\textit{Categories that are more frequent after a negative interruption}} \\
    \hline 
high-nav & 7.84 & \textbf{10.14} & 8.74  \\
find-replace & 1.26 & \textbf{1.47} & 1.11 \\
debug & 3.08 & \textbf{7.81} & 6.35  \\
search & 0.57 & \textbf{0.96} & 0.73 \\
clean-build & 0.42 & \textbf{0.62} & 0.56  \\
    \hline 
\multicolumn{4}{c}{\textit{Categories that are less frequent during the recovery time}} \\
    \hline 
text-nav & 14.20 & 12.89 & \textbf{16.13} \\
control & 1.21 & 1.75 & \textbf{1.82} \\
\hline
\end{tabular}
\end{table}
